When environmentally persistent pathogens transform good habitat into ecological traps

### 2015-12-04 Manuscript/manuscript.tex
SPOM assumptions and justification in methods

To address the above questions, we developed a stochastic patch occupancy model (SPOM) in which each patch can be in one of three possible states: occupied by susceptible hosts (S), occupied by infectious hosts (I), and unoccupied by the host ($\emptyset$).  State transitions are governed by host colonization, extinction, and transmission rates, where a susceptible population can become infectious either through direct contact with infectious immigrants, or through a local environmental pathogen reservoir (Table~\ref{transitions}).

>>>>

To address the above questions, we developed a model based on the stochastic patch occupancy model (SPOM) framework.
This approach, based on a well-developed body of theory, models the occupancy state of discrete patches of suitable habitat.
Though this prevents us from modeling the dynamics of local populations, this approach is able to capture realistic spatial structure while remaining relatively tractable (\cite{Ovaskainen2004}).
To incorporate disease transmission, we expand on existing SPOM models and allow each patch to be in one of three possible states: occupied by susceptible hosts (S), occupied by infectious hosts (I), and unoccupied by the host ($\emptyset$).  State transitions are governed by host colonization, extinction, and transmission rates, where a susceptible population can become infectious either through direct contact with infectious immigrants, or through a local environmental pathogen reservoir (Table~\ref{transitions}).
